% References
\begin{thebibliography}{99}

\bibitem{react}
React Documentation, "React - A JavaScript library for building user interfaces," Meta Platforms Inc., 2024. [Online]. Available: https://react.dev/

\bibitem{nodejs}
Node.js Foundation, "Node.js Documentation," 2024. [Online]. Available: https://nodejs.org/

\bibitem{mongodb}
MongoDB Inc., "MongoDB Manual," 2024. [Online]. Available: https://www.mongodb.com/docs/

\bibitem{express}
StrongLoop, "Express - Fast, unopinionated, minimalist web framework for Node.js," 2024. [Online]. Available: https://expressjs.com/

\bibitem{typescript}
Microsoft Corporation, "TypeScript Documentation," 2024. [Online]. Available: https://www.typescriptlang.org/

\bibitem{tailwind}
Tailwind Labs, "Tailwind CSS Framework," 2024. [Online]. Available: https://tailwindcss.com/

\bibitem{jwt}
M. Jones, J. Bradley, and N. Sakimura, "JSON Web Token (JWT)," RFC 7519, May 2015.

\bibitem{agile}
K. Beck et al., "Manifesto for Agile Software Development," 2001. [Online]. Available: https://agilemanifesto.org/

\bibitem{rest}
R. T. Fielding, "Architectural Styles and the Design of Network-based Software Architectures," PhD dissertation, University of California, Irvine, 2000.

\bibitem{mern}
A. Subramanian, "Pro MERN Stack: Full Stack Web App Development," 2nd ed., Apress, 2019.

\bibitem{testing}
G. J. Myers, C. Sandler, and T. Badgett, "The Art of Software Testing," 3rd ed., John Wiley \& Sons, 2011.

\bibitem{softeng}
I. Sommerville, "Software Engineering," 10th ed., Pearson Education, 2015.

\bibitem{schedule}
M. L. Pinedo, "Scheduling: Theory, Algorithms, and Systems," 5th ed., Springer, 2016.

\end{thebibliography}
